\subsection{Microcontroller Testing}
Our testing plan for the microcontroller will mostly revolve around attempting to perform various simple tasks and checking if they work. First, we will test if we are able to power the microcontroller on. Next, we will begin testing the functionality of the part. One of these tasks will be to see if we can program the microcontroller over the programming pins. We will write a simple program that turns on and blinks them. Another task will be to see if we can send AT commands to the on board LoRa module.

\subsection{Sensor Test Plan}
When it comes to testing the sensors we must be very thorough and diligent. While every portion of the system is important this is what every other sub system is designed around and for. Should errors persist within any sensor the entire network could be compromised with inaccurate and inconsistent information. The sensors have different needs and functionalities so as a result testing for this system needs to be unique for each and every component.

\subsubsection{SPS30 Sensor}
When it comes to testing this sensor we must take several factors into account. Fist of all every subsystem must be tested before this. If it turns out the power subsystem is providing too much or too little power then the sensor could be damaged or not turn on at all. If the microcontroller is damaged then it may not interpret the results correctly. If the communication system is faulty then we may receive incorrect, unreadable, or no response at all. Once we've verified that every other subsystem is correct then and only then is it proper to proceed in testing any sensor.
For a good rule of thumb one should access and make sure that all the wiring's are correct before proceeding with testing the SPS30, one should also take advantage of the convenient testing point on the sensor side of the power rail to ensure that the input voltage is the correct five volts.

To properly test the SPS30 a one cubic meter containment field must be constructed that is airtight. From there exactly thirty five grams of finely ground sawdust must be introduced with aid of a fan to thoroughly mix the particulates throughout the containment. The SPS30 will then be powered on to observe the readings and find the accuracy.

\subsubsection{ZMOD4510 Sensor}
When it comes to testing this sensor we must take several factors into account. Fist of all every subsystem must be tested before this. If it turns out the power subsystem is providing too much or too little power then the sensor could be damaged or not turn on at all. If the microcontroller is damaged then it may not interpret the results correctly. If the communication system is faulty then we may receive incorrect, unreadable, or no response at all. Once we've verified that every other subsystem is correct then and only then is it proper to proceed in testing any sensor.
For the Renesas sensor our priority is testing nitrogen dioxide and ozone levels in the air. Once again we will use the constructed containment field and will introduce these 2 gases over a period over an hour and record the results and compare them to the concentration of gases introduced. At market nitrogen dioxide can be purchased at a concentration of 10 ppm and an ozone generator can be purchased that will produce 5 grams of ozone per hour. With both of these sources we can reasonably test the capabilities of the Renesas sensor to determine its functionality.

\subsubsection{BME688 Sensor}
When it comes to testing this sensor we must take several factors into account. Fist of all every subsystem must be tested before this. If it turns out the power subsystem is providing too much or too little power then the sensor could be damaged or not turn on at all. If the microcontroller is damaged then it may not interpret the results correctly. If the communication system is faulty then we may receive incorrect, unreadable, or no response at all. Once we've verified that every other subsystem is correct then and only then is it proper to proceed in testing any sensor.
The Bosch in particular will require a number of tests to demonstrate that it is properly working. The first test well describe is of its humidity sensor applications. An independent humidity tester will be brought in for this to compare results. Once again utilizing an airtight one cubic meter containment field we will place both the module and an independent humidity tester. After that a pot of steaming water will be introduced that will add a source of humidity and the containment field will be closed. For one hour both tester will take readings as the humidity quickly increases and slowly goes back to normal levels. Should the unit and the independent testers reading stay within the 3 percent range described by the manufacturer then we know that functionality of the sensor is correct.
The next testing method we will implement is that of the carbon monoxide sensor functionality. The first step would be the acquisition of a sealed container of carbon monoxide. Several are available with gas densities reaching 0.0012g/cubic centimeter. Enough of this source will be acquired to fill the one cubic meter containment field. Once the field has been filled the unit will be placed inside and take measurements and should the unit give back a measurement within acceptable ranges of the gas then this functionality will be confirmed to be working.

\subsection{Power System Testing}
The essential elements of testing our power sub system can be described as basic and comprehensive. If any single element were to introduce a factor to limit or boost power unexpectedly certain components may not function or become damaged beyond repair. As a result the upmost care must be taken into account when testing the power subsystems of the device. The most effective method of testing in our opinion is to monitor the voltage and current starting at the power sources going all the way to the load. 

\subsubsection{Source Testing}
The first step we will undergo would be to test the solar panel. This will be done by using the panel and a voltmeter, one would take the solar panel out during both the most and least ideal conditions. This would mean taking it out on both a sunny and overcast day and monitoring the output over the course over an eight to ten-hour period. This will provide us with an accurate and predictable range of our primary source. This will also alert us of any anomalies that could be present weather that be alarmingly low or high input voltages. Once we have complied information from this test and it matches the expected input we can continue on in our process of testing more components within the subsystem.

The next step to testing our sources would be to test the USB input. This is a far bit simpler as the USB input would have a standard input we could compare it to and any difference would indicate an inconsistent or unreliable element. Additionally we don't have to worry about a fluctuation in power as the USB input would stay steady at all times and any fluctuation would also indicate an undesirable element. Once again using a voltmeter once the USB charger has been powered on we can monitor the connection several times over the course of an hour to check its consistency. For ease of use testing points have been added at select points that can be used, these points can be found in the schematic and are the points we will be using to test this subsystem. Once we've verified that the USB has expected and consistent power we can continue on in our process of testing more components within the subsystem.

\subsubsection{IC Testing}
When we get to the IC a new approach must be made. First, when monitoring the input from the sources care must be made to monitor the readings directly at the input of the IC as well as the output reading directly from the sources. This will tell us if there is a factor manipulating the power before it reaches its destination. The next step would be to observe the ICs output voltage. Now due to the nature of the system the input voltage of the IC may vary, but the same cannot be said about the output voltage. The next step would be to observe the output voltage of the IC as the solar panels input voltage changes. Should the output voltage change in sizeable way then the IC is not accomplishing one of its core purposes and should be examined and repaired or replaced. 

For ease of use, testing points have been added at select points that can be used, these points can be found in the schematic and are the points we will be using to test this subsystem. The next test that will be implemented will be for the other functions of the IC. For example the IC is supposed to begin drawing power from the battery when no other source is present so when the battery is charged the solar panel will be removed from all light sources and the USB will be disconnected. If the battery begins powering the system then we will have verified this function of the IC. From there the battery will be constantly depleted to see if the IC will identify a low battery. If the output voltage of the battery is low then we can confirm independently that it has a low charge and the IC should indicate as such. If it does then this function is confirmed.

\subsubsection{Battery Testing}
Battery testing must be undertaken in a thorough and unique way. Once we have verified the consistency of the output of the IC, we can observe the activity of the battery and identify and unexpected or unplanned elements. Ideally, the best way to test this portion of the subsystem would be to charge the battery with a 4.2V output and observe the charge curve of the battery during the charging process. Should the charge curve present itself unlike the example in the power subsection, then several issues could be at fault. 

For instance, if the battery is charging and discharging faster than expected then potentially the electrolyte mixture in the battery could be compromised. Once we have observed a stable and predictable charge curve, the next step would be to observe the discharge curve. Just like testing the charge curve, one will have to use a voltmeter over the course over a few hours to collect data and then graph a discharge curve and compare it to the example graph in the power subsection. Once we've verified that the battery can properly charge and discharge, is getting the proper charge voltage, and is discharging when the original sources are not present or flowing through the IC then we've verified that the battery is functioning properly and can move on to other components. For ease of use, testing points have been added at select points in our design. These points can be found in the schematic and are the points we will be using to test this subsystem.

\subsubsection{Power Rail Testing}
Power rail testing is more straight forward. At this point, we have covered the sources, the IC, the battery, and all the connections in between. Should the rest of the system be predictable, stable, and expected now comes the load itself. The power rails comfortably change the voltage from the IC and battery to the voltage needed for every component. 

The most straightforward way to test the railing would be to use a voltmeter and observe the voltage at the output of the IC and battery to verify that it is indeed correct.
Next, you would observe that the input voltage of each power rail is the same as the output voltage you just measured. If that is not the case, then an element may be present in the connection leading to the difference and the up most care should be taken to discerning the reason behind the change. Finally, for each power rail you would need to ensure that the output voltage of the rail is as predicted. For ease of use, testing points have been added at select points in our design. These points can be found in the schematic and are the points we will be using to test this subsystem.
