\section{Testing}

\subsection{Hardware Testing}
    \subsubsection{Hardware Testing Overview}
    \subsubsection{Microcontroller Testing}
    \subsubsection{Sensor Testing}
    \subsubsection{Power Sub-system Testing}
    The essential elements of testing our power sub system can be described as basic and comprehensive. If any single element were to introduce a factor to limit or boost power unexpectedly certain components may not function or become damaged beyond repair. As a result the upmost care must be taken into account when testing the power subsystems of the device. The most effective method of testing in our opinion is to monitor the voltage and current starting at the power sources going all the way to the load. 
    \subsubsubsection{Source Testing}
    The first step we will undergo would be to test the solar panel. This will be done by using the panel and a voltmeter, one would take the solar panel out during both the most and least ideal conditions. This would mean taking it out on both a sunny and overcast day and monitoring the output over the course over an eight to ten hour period. This will provide us with an accurate and predictable range of our primary source. This will also alert us of any anomalies that could be present weather that be alarmingly low or high input voltages. Once we have complied information from this test and it matches the expected input we can carry on and test further into the subsystem.
    The next step to testing our sources would be to test the USB input. This is a far bit simpler as the USB input would have a standard input we could compare it to and any difference would indicate an inconsistent or unreliable element. Additionally we don't have to worry about a fluctuation in power as the USB input would stay steady at all times and any fluctuation would also indicate an undesirable element. Once again using a voltmeter once the USB charger has been powered on we can monitor the connection several times over the course of an hour to check its consistency. Once we've verified that the USB has expected and consistent power we can carry on testing further into the power subsystem.
    \subsubsubsection{IC Testing}
    When we get to the IC a new approach must be made. First When monitoring the input from the sources care must be made to monitor the readings directly at the input of the IC as well as the output reading directly from the sources. This will tell us if there is a factor manipulating the power before it reaches its destination. The next step would be to observe the ICs output voltage. Now due to the nature of the system the input voltage of the IC may vary but the same cannot be said about the output voltage. The next step would be to observe the output voltage of the IC as the solar panels input voltage changes. Should the output voltage change in sizeable way then the IC is not accomplishing one of its core purposes and should be examined and repaired or replaced. The next test that will be implimented will be for the other functions of the IC.......
    

